\documentstyle[10pt]{letter}

%%%%%% Letter Size Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%        \addtolength{\textwidth}{2.5cm}     %% For longer or shorter text width
        \addtolength{\topmargin}{-4.0cm}    %% For more or less top margin
       \addtolength{\textheight}{7.5cm}    %% For longer or shorter textheight
%        \addtolength{\oddsidemargin}{-1.25cm} %% For odd side margin (twoside)
                                            %% or margin (oneside)

\address{Jean Ragusa\\ 
Department of Nuclear Engineering \\
Texas A\&M University\\
College Station, TX 77843-3133, USA\\
phone: (979) 862 2033\\
e-mail: jean.ragusa@tamu.edu \vspace{0.5cm}}

%%%%%% The Signature  and Date %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\signature{\vspace{-1.25cm}Marc Delchini, Jean Ragusa}   


\begin{document}

\begin{letter}{
    Editor,\\
    International Journal for Numerical Methods in Fluids}
\date{\today}
%%%%%% More vertical space can be added here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%         \vspace{3.0cm}

\opening{Dear Editor,}
         \vspace{0.25cm}
%%%%%% More vertical space can be added here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Please find attached a copy of our manuscript titled ``Viscous Regularization of the non-equilibrium Grey Radiation-Hydrodynamics'' for submission to the IJNMF. 

In this paper, we extend the entropy-based stabilization, a viscous regularization based on the entropy production and devised by Guermond et al. for Euler equations, to the radiation hydrodynamics (RH) equations with grey non-equilibrium diffusion. Previously, we were only able to demonstrate that the entropy viscosity method was a suitable regularization for the hyperbolic parts of the RH equations. Here, we show that an entropy condition is obtained for the full RH equations. 

Numerical results are presented for a Mach-3 radiative shock simulation, with constant and material-dependent opacities. The numerical solutions are in excellent agreement with semi-analytical solutions. Physical features such as embedded hydrodynamic shocks and the Zeldovich spike are resolved accurately without spurious oscillations. 

Thank you for considering this manuscript for publication in the special issue of IJNMF dedicated to research papers presented at MULTIMAT 2015.

%\vspace{-0.25cm}


%%%%%% More vertical space can be added here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%% The Closing %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\closing{Best regards, }

\end{letter}
\end{document}

